## load the diamonds data set
```{r}
library(ggplot2)
data("diamonds")
```

## You should notice that the diamonds data set will be listed as a 'Promise' in the workspace. This is a special object in R, and you need to run a command on the data to fully load the data set. Try running a summary:
```{r}
summary(diamonds)
```
## You can learn more about the diamonds data set by typing
```{r}
?diamonds
diamonds$color
```

# Create a histogram of the price of
# all the diamonds in the diamond data set.
```{r}
ggplot(data = diamonds, aes(x = diamonds$price)) +
  geom_histogram(bins = 400)

summary(diamonds$price)
```
## Diamonds Counts
```{r}
summary(diamonds$price<500)
summary(diamonds$price<250)
summary(diamonds$price>15000)
```

## Cheaper diamonds
```{r}
ggplot(diamonds, aes(x = diamonds$price)) +
  geom_histogram(bins = 10) +
  scale_x_continuous(limits = c(0, 2000))
ggsave("priceHistogram.png")
```
## Price by Cut Histograms
```{r}
ggplot(diamonds, aes(x = diamonds$price)) +
  geom_histogram(bins = 30) +
  scale_x_continuous(limits = c(0, 20000)) + 
  facet_wrap(~cut, scales='free')
ggsave("priceHistogram by cut.png")
```

## Price per carat
```{r}
ggplot(diamonds, aes(x = price/carat)) +
  geom_histogram(bins=30) +
  facet_wrap(~cut, scales = "free") +
  scale_x_log10()
```

## Price box plot
```{r}
ggplot(diamonds, aes(x=color, y = price)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 8000))
by(diamonds$price, diamonds$color, summary)
IQR(subset(diamonds, color=='D')$price)
IQR(subset(diamonds, color=='J')$price)
```

## Price per carat box plot by color

```{r}
ggplot(diamonds, aes(x=color, y=price/carat)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 7000))
```
## Carat frequency polygon
```{r}
ggplot(aes(x=price), data=diamonds) +
  geom_freqpoly(aes(color=carat))
```

